More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-11-14 2016-Weak-FH-Bisim/WeakBisim.tex
improved proof notations: s,t,u and removed target

       	It is trivial to check reflexivity and symmetry. Here we focus on the
       	transitivity. 
       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
       	prove 
       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s^1$, $s^2$, $s^3$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s^i_x$ is in the 
       	states of 
       		$\mathcal{T}_i$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s^1,s^2|\Pred)$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
       	form 
       	$(s^2,s^3|\Pred\,')$.

       	Let $\mathcal{R}''$ be the relation: 
       	\[\mathcal{R}'' = \{(s^1,s^3|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
       		(s^1,s^2|\Pred)\in\mathcal{R}\\ (s^2,s^3|\Pred\,')\in\mathcal{R}' 	
       		\end{array}
       	}\,\Pred\land\Pred\,'\}\]

@@

       	The relation is built as follows: for each pair of state $s^1$, $s^3$, for each 
       	state 
       	$s^2$ such that $\mathcal{R}$ relates $s^1$ and $s^2$, and $\mathcal{R}'$ relates 
       	$s^2$ 
       	and $s^3$, we take the conjunction of the two predicates. The predicates for 
       	different 
       	values of $s^2$ are collected by a disjunction.

       	We will show
       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
       	$(s^1,s^3|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
       	$\mathcal{T}_2$ relating $s^1$ and $s^3$, let $(s^2_p)^{p\in P}$ be this family.

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s^1,s^2_p|\Pred_p)\in\mathcal{R}$,  and 
       	$(s^2_p,s^3|\Pred\,'_p)\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation.
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s^1$.
       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
       	\begin{mathpar}

       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^1_i\xrightarrow{a_i}_i {s^{1}}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
       		%States(I_1)
       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s^1 \OTarrow {v} {s^{1}}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{2}_{pi}\xrightarrow{a_{p i x}}_i s^{2}_{p i x}\}^{i\in I_{2 p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{s^2_p \OTarrow {v_{px}} s^{2}_{px}}
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, J_1=J_{2px}, (s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in 
       	\mathcal{R}$;
       	and  \\

       	$\Pred_p \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land v\!=\!v_{px} \land
       	\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$

       	for any open transition $OT_{px}$, since
       	$(s^2_p,s^3|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{s^{3}_i\xrightarrow{a_{i p x y}}_i s^{3}_{i p x y}\}^{i\in I_{3 p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{s^3 \OTarrow {v_{pxy}} s^{3}_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{2px}=J_{3pxy}, 
       	(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.

@@

		One can notice that, as bisimulation predicates are used to relate states that 
		belong to two different open automata, the free variables of these predicates 
		that do not belong to the two related automata can safely be renamed to avoid any 
		name clash. In practice,
       	we can suppose that, as $\Pred\,'_{target_{pxy}}$ is used to relate states of 
       	$\mathcal{T}_1$, and $\mathcal{T}_3$, there exists a predicate obtained by 
       	renaming variables, that is equivalent to $\Pred\,'_{target_{pxy}}$ and does not 
       	contain the variables of 	$\mathcal{T}_2$. This predicate with ``fresh'' 
       	variables is called   $\Pred\,'_{target_{pxy}}$ in the following.
       	Similarly, we can suppose that $\Pred_{target_{px}}$ contains no 
       	variable in $\mathcal{T}_3$, and $\Pred_{target_{pxy}}$ contains no 
       	variable in $\mathcal{T}_1$.

       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
       	({s^{1}}',s^{3}_{pxy}|\Pred\,'_{target_{pxy}})\in \mathcal{R}''$. 
       	Indeed for any 
       	$p$, 
       	$x$, and 
       	$y$, $s^2_{px}$
       	relate ${s^{1}}'$ and $s^{3}_{pxy}$, indeed
       	$(s^{1'},s^{2}_{px}|\Pred_{target_{px}})\in \mathcal{R}$
       	and $(s^{2}_x,s^{3}_{pxy}|\Pred_{target_{pxy}})\in \mathcal{R}'$. 
       	More precisely, $s^{2}_{px} \in ({s^{2}_p}')^{p\in P'}$ where $({s^{2}_p}')^{p\in 
       		P'}$ 
       	is 
       	the set of states relating ${s^{1}}'$ and $s^{3}_{pxy}$.
       	Consequently, for all $p$, $x$, $y$, $\Pred_{target_{px}}\land 
       	\Pred_{target_{pxy}}\implies 
       	\Pred\,'_{target_{pxy}}$ (this is one element of the  disjunction defining the 
       	predicate 
       	relating ${s^{1}}'$ and $s^{3}_{pxy}$ in the definition of $\mathcal{R}''$).

       	Second, we need \\
       	\begin{small}
       		$\Pred\,'' \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

       	We have, for all $p$
       	\begin{small}
       		$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
       		\land v\!=\!v_{px} \land
       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

By construction, the Post substitutions only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{target_{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= 
       	\Pred_{target_{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= \Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $

       	This allows us to conclude, with $\Pred\,'' = \bigvee_{p\in P} 
       	\Pred_p\land\Pred_p\,'$:
         	\begin{small}     	
$\Pred\,'' \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
\Pred_p\land\Pred_p\,' \land \Pred_{OT})\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
\Rightarrow \big( 
\Pred_{OT_{pxy}}
\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land v\!=\!v_{pxy} \land
\Pred\,'_{target_{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
  \end{small}

       	\smallskip
       	Concerning the other direction of bisimulation, it is sufficient to notice that 
       	the role 
       	of $s^1$ and $s^3$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
       	the 
       	proof is similar.

>>>>

       	It is trivial to check reflexivity and symmetry. Here we focus on the
       	transitivity. 
       	To prove transitivity of strong FH-bisimulation on pNets it is sufficient to 
       	prove 
       	transitivity of the strong FH-bisimulation on states. Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
       	in the 
       	states of 
       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s,t|\Pred)$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
       	form 
       	$(t,u|\Pred\,')$.

       	Let $\mathcal{R}''$ be the relation: 
       	\[\mathcal{R}'' = 
       	\{(s,u|\Pred\,'')\,\,\Big|\,\Pred\,''=\bigvee_{\begin{array}{c}       		
       		(s,t|\Pred)\in\mathcal{R}\\ (t,u|\Pred\,')\in\mathcal{R}' 	
       		\end{array}
       	}\,\Pred\land\Pred\,'\}\]

@@

       	The relation is built as follows: for each pair of state $s$, $u$, for each 
       	state 
       	$t$ such that $\mathcal{R}$ relates $s$ and $t$, and $\mathcal{R}'$ relates 
       	$t$ 
       	and $u$, we take the conjunction of the two predicates. The predicates for 
       	different 
       	values of $t$ are collected by a disjunction.

       	We will show
       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
       	$(s,u|\Pred\,'')\in\mathcal{R}''$. Then there is a set of states of 
       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s,t_p|\Pred_p)\in\mathcal{R}$,  and 
       	$(t_p,u|\Pred\,'_p)\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation.
       	For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	Additionally we have $\Pred\,'' = \bigvee_{p\in P} \Pred_p\land\Pred_p\,'$.
       	\begin{mathpar}

       	\inferrule*[myfraction=\reddottedrule]
       	{\{s_i\xrightarrow{a_i}_i {s}'_i\}^{i\in I_1}, % , s^1_i,s^{1'}_i\in
       		%States(I_1)
       		\{\xrightarrow{b_j}_j\}^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {v} {s}'}

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{t_{p i}\xrightarrow{a_{p i x}}_i t_{p i x}\}^{i\in I_{2 p x}},
       		\{\xrightarrow{b_{j p x}}_j\}^{j\in J_{2px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t_p \OTarrow {v_{px}} t_{p x}}
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, J_1=J_{2px}, (s',t_{px}|\Pred_{{px}})\in 
       	\mathcal{R}$;
       	and  \\

       	$\Pred_p \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       	\land v\!=\!v_{px} \land
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$

       	for any open transition $OT_{px}$, since
       	$(t_p,u|\Pred\,^\prime_p)\in\mathcal{R}'$ there exist open transitions
       	$OT_{pxy}^{y\in Y} \subseteq \mathcal{T}_3$:

@@

       	%    \left( fresh \ \overline{a_i}, \overline{b_j}, v_x.\ \
       	\inferrule*[myfraction=\reddottedrule]
       	{\{u_i\xrightarrow{a_{i p x y}}_i u_{i p x y}\}^{i\in I_{3 p x y}},
       		\{\xrightarrow{b_{j p x y}}_j\}^{j\in J_{3pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTarrow {v_{pxy}} u_{pxy}}
       	%         \right)

       	\end{mathpar}
       	such that  $\forall y, J_{2px}=J_{3pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred\,'_p \land \Pred_{OT_{p x}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. b_{jpx}=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land v_{px}\!=\!v_{pxy} \land
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.

@@

       	First, $\forall y, \forall x, \forall p, J_1=J_{2px}=J_{3pxy}, 
       	({s}',s_{pxy}|\Pred\,'_{{pxy}})\in \mathcal{R}''$. 
       	Indeed for any 
       	$p$, 
       	$x$, and 
       	$y$, $t_{px}$
       	relate ${s}'$ and $u_{pxy}$, indeed
       	$(s',t_{px}|\Pred_{{px}})\in \mathcal{R}$
       	and $(t_{px},u_{pxy}|\Pred{{pxy}})\in \mathcal{R}'$. 
       	More precisely, $t_{px} \in ({t_p}')^{p\in P'}$ where $({t_p}')^{p\in 
       		P'}$ 
       	is 
       	the set of states relating ${s}'$ and $u_{pxy}$.
       	Consequently, for all $p$, $x$, $y$, $\Pred_{px}\land 
       	\Pred_{{pxy}}\implies 
       	\Pred\,'_{{pxy}}$ (this is one element of the  disjunction defining the 
       	predicate 
       	relating ${s}'$ and $u_{pxy}$ in the definition of $\mathcal{R}''$).

One can notice that, as bisimulation predicates are used to relate states that 
belong to two different open automata, the free variables of these predicates 
that do not belong to the two related automata can safely be renamed to avoid any 
name clash. In practice,
we can suppose that, as $\Pred\,'_{{pxy}}$ is used to relate states of 
$\mathcal{T}_1$, and $\mathcal{T}_3$, there exists a predicate obtained by 
renaming variables, that is equivalent to $\Pred\,'_{{pxy}}$ and does not 
contain the variables of 	$\mathcal{T}_2$. This predicate with ``fresh'' 
variables is called   $\Pred\,'_{{pxy}}$ in the following.
Similarly, we can suppose that $\Pred_{{px}}$ contains no 
variable in $\mathcal{T}_3$, and $\Pred_{{pxy}}$ contains no 
variable in $\mathcal{T}_1$.

       	Second, we need \\
       	\begin{small}
       		$\Pred\,'' \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
       		\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v\!=\!v_{pxy} \land
       		\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

       	We have, for all $p$
       	\begin{small}
       		$\Pred_p \land \Pred_{OT}\land\Pred'_p\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\land\Pred'_p\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\left( \forall j. b_j=b_{jpx}  \Rightarrow (\Pred_{OT_{px}}\land\Pred'_p)
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       		\big( \forall j. b_j=b_{jpx}  \Rightarrow (\bigvee_{y\in Y} 
       		\big( \forall j'. b_{j'px}=b_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\big))
       		\land v\!=\!v_{px} \land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X} \bigvee_{y\in Y}
       		\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
       		\Rightarrow \big( 
       		\Pred_{OT_{pxy}}
       		\land v\!=v_{px}\!=\!v_{pxy}\\\hspace{3em}~ \land
       		\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
       		\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\big)\big)
       		$

@@

By construction, the Post substitutions only have an effect on the  
variables of the open automaton they belong to, they also produce terms containing only 
variables of the open automaton they belong to. Finally, because of the domain of the 
substitutions  and of the predicates, we have:\\
       	$\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= 
       	\Pred_{{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       	\Pred_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	\implies\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\\
       	= \Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $

       	This allows us to conclude, with $\Pred\,'' = \bigvee_{p\in P} 
       	\Pred_p\land\Pred_p\,'$:
         	\begin{small}     	
$\Pred\,'' \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} (
\Pred_p\land\Pred_p\,' \land \Pred_{OT})\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}
 \bigvee_{x\in X} \bigvee_{y\in Y}
\big( \forall j, j'. b_j=b_{jpx} \land b_{j'px}=b_{j'pxy}
\Rightarrow \big( 
\Pred_{OT_{pxy}}
\land v\!=v_{px}\!=\!v_{pxy}\\~\hspace{3em}~ \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\big)\big)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\bigvee_{y\in Y}\bigvee_{p\in P}
\left( \forall j. b_j=b_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land v\!=\!v_{pxy} \land
\Pred\,'_{{pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
  \end{small}

       	\smallskip
       	Concerning the other direction of bisimulation, it is sufficient to notice that 
       	the role 
       	of $s$ and $u$ in the definition of $\mathcal{R}''$ is symmetrical, and thus 
       	the 
       	proof is similar.
